Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-05-16 TEBenchmarkPaper/article.tex
TEB: "Final" final, last, finished, done (honest this time!) changes (yeah right...)

Given a sample of definitions and a corresponding ground truth, the actual
execution of the MTE tool proceeds as in prior work. We must translate the
chosen definitions into the required input format, then we time the execution
with a timeout (e.g. 5 minutes).

@@

\begin{table}
  \centering
  \begin{tabular}{ |r|l| }
    \hline
    \bfseries Sample Size & \bfseries Speedup
    \csvreader[]{speedups.csv}{}
    {\\\hline\csvcoli&\csvcolii} \\
    \hline
  \end{tabular}
  \caption{Speed up from using QuickSpec compared to IsaCoSy, as reported by
    Speedup-Test for a confidence level of 95\%. Sizes 1 and 2 were not
    considered statistically significant due to having less than 30 samples.
    These are conservative estimates, since the 300 second time limit acts to
    reduce the measured time difference.}
  \label{table:speedups}
\end{table}

>>>>

Given a sample of definitions and a corresponding ground truth, the actual
execution of the MTE tool proceeds as in prior work. We must translate the
chosen definitions into the required input format, then we time the execution
with a timeout (e.g. 5 minutes). We use wall-clock time since this is most
relevant to a user's experience, it has a straightforward interpretation and
tracking it does not require intrusive alterations to a tool's implementation.
The downside is that comparisons must take hardware performance into account,
which would not be the case if time were measured by some proxy like number of
expressions evaluated.

@@

\begin{table}
  \centering
  \begin{tabular}{ |r|l| }
    \hline
    \bfseries Sample Size & \bfseries Speedup
    \csvreader[]{speedups.csv}{}
    {\\\hline\csvcoli&\csvcolii} \\
    \hline
  \end{tabular}
  \caption{Speedup from using QuickSpec compared to IsaCoSy, i.e. the median
    time taken by IsaCoSy divided by that of QuickSpec. All were deemed
    statistically significant QuickSpec was significantly faster
    ($\alpha = 0.05$) for all sizes, except 1 and 2 due to too few samples.
    These are conservative estimates, since the 300 second time limit acts to
    reduce the measured time difference (e.g. sizes 13 and 20, where the median
    for both tools timed out).}
  \label{table:speedups}
\end{table}
